Characterize the fetal kidney reference from the kidney cell atlas

### 2024-10-16 analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd
fix relative path

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
  fetal_kidney_path: "scratch/fetal_kidney.rds"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---

>>>>

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
  fetal_kidney_path: "../scratch/fetal_kidney.rds"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---
